Incentivizing Exploration by Heterogeneous Users

### 2018-06-06 problem_setting.tex

At each time $t$, a new user (or \emph{agent}) arrives,
whose feature vector (which we also call his \emph{type})
$\AgentV{t} \in \R^d$ is drawn from a known distribution \AgentDist.
Depending on context, we will identify agents with their arrival time
$t$ or their type \AgentV{t}.
When agent $t$ pulls arm $\Pull{t} := i$,
he and all future agents observe a vector
$\ObsV{t} = \ArmV{i} + \NoiseV[t]$ for arm $i$,
and his reward is $\AgentV{t} \cdot \ObsV{t}$,
i.e., agents have linear preferences.
Although the model is linear, it permits additional flexibility
through the addition of derived attributes that are nonlinear
transformation of some original attribute vector.
One can simply define \dkedit{$\Ag{j} = h_j(\AgV)$ for some known
nonlinear functions $h_j$} and $j=d+1,\ldots,d'$, and then increase the
number of attributes to $d'$.

>>>>

At each time $t$, a new user (or \emph{agent}) arrives,
whose feature vector (which we also call his \emph{type})
$\AgentV{t} \in \R^d$ is drawn from a known distribution \AgentDist.
Depending on context, we will identify agents with their arrival time
$t$ or their type \AgentV{t}.
When agent $t$ pulls arm $\Pull{t} := i$,
he and all future agents observe a vector
$\ObsV{t} = \ArmV{i} + \NoiseV[t]$ for arm $i$,
and his reward is $\AgentV{t} \cdot \ObsV{t}$,
i.e., agents have linear preferences.
Although the model is linear, it permits additional flexibility
through the addition of derived attributes that are nonlinear
transformation of some original attribute vector.
One can simply define $\Ag{j} = h_j(\AgV)$ for some known
nonlinear functions $h_j$ and $j=d+1,\ldots,d'$, and then increase the
number of attributes to $d'$.
